%% ============================================================
%%  chapters/04_college_selection.tex
%%  Chapter 4: College & Branch Selection
%% ============================================================

\chapter{College \& Branch Selection}
\label{chap:college}

%% ─────────────────────────────────────────────────────────
\section{Top Institutes for VLSI / ECE}
\label{sec:top-institutes}

\begin{tblr}{
    colspec = {X[1,c] X[2,l] X[5,l]},
    hlines, vlines,
    row{1} = {bg=pfBlue, fg=white, font=\sffamily\bfseries},
    row{2,4,6} = {bg=pfGrey},
  }
  \toprule
  Tier & Institutes & Key Strengths \\
  \midrule
  \textbf{Tier 1}
    & \inst{IISc}, \inst{IIT Bombay}, \inst{IIT Madras},
      \inst{IIT Delhi}, \inst{IIT Kanpur}
    & Best industry connections, research output, placement
      records, and faculty quality. \\
  \textbf{Tier 2}
    & \inst{IIT Kharagpur}, \inst{IIT Roorkee}, \inst{IIT Hyderabad}
    & Strong placements; IITH stands out among emerging IITs
      for placement, infrastructure, and teaching. \\
  \textbf{Tier 3}
    & Remaining IITs
    & Vary significantly; check recent placement data per branch. \\
  \bottomrule
\end{tblr}

%% ─────────────────────────────────────────────────────────
\section{Best IIT for Analog Roles}
\label{sec:analog-iit}

\begin{protip}[Analog Domain Recommendation]
  \textbf{\inst{IIT Madras}} is the premier choice for analog roles in placements
  and research. It has dedicated labs in RF, mixed-signal, and analog IC design,
  strong faculty with industry collaborations, and a track record of placing
  students in top semiconductor companies.
\end{protip}

%% ─────────────────────────────────────────────────────────
\section{Top Courses at IISc by Placement}
\label{sec:iisc-courses}

\begin{tblr}{
    colspec = {X[3,l] X[4,l]},
    hlines, vlines,
    row{1} = {bg=pfBlue, fg=white, font=\sffamily\bfseries},
    row{2,4} = {bg=pfGrey},
  }
  \toprule
  Institute & Top Branches (Placement-wise) \\
  \midrule
  \inst{IISc Bangalore}
    & CSE, AI, CDS, MVLSI, ESE, ECE, Signal Processing \\
  \inst{IITs (general)}
    & CSE, Data Science, VLSI, ICS, ESE \\
  \bottomrule
\end{tblr}

%% ─────────────────────────────────────────────────────────
\section{Pure VLSI vs.\ Related Fields}
\label{sec:vlsi-vs-related}

\begin{faqentry}{Which field is better: pure VLSI or related fields like
  Electronic System Design (ESD) or Solid-State Devices?}
  \textbf{Pure VLSI} tends to be stronger in terms of campus placements.
  ESD/Signal Processing branches also have good placements at the top institutes.
  However, choice should ultimately be driven by \textbf{individual interest} and
  long-term career goals. Forced branch selection leads to poor academic
  performance.
\end{faqentry}

\begin{faqentry}{Should I choose Signal Processing at older IITs or VLSI at
  newer ones?}
  This depends on your personal interest. If you are passionate about Signal
  Processing, a strong older IIT is the better environment despite the branch.
  Placement data at newer IITs in VLSI has been improving but the faculty and
  research ecosystem of older IITs generally remains superior. Evaluate the
  specific institute's recent placement records.
\end{faqentry}

%% ─────────────────────────────────────────────────────────
\section{NIT Trichy (Communication) vs.\ NIT Calicut (VLSI)}
\label{sec:nit-comparison}

Both are strong institutes. Consider the following:

\begin{tblr}{
    colspec = {X[2,l] X[3,l] X[3,l]},
    hlines, vlines,
    row{1} = {bg=pfBlue, fg=white, font=\sffamily\bfseries},
    row{2} = {bg=pfGrey},
  }
  \toprule
  Factor & NIT Trichy -- Communication & NIT Calicut -- VLSI \\
  \midrule
  Domain
    & Signal Processing, Wireless, Systems
    & Semiconductor design, CMOS, FPGA \\
  Industry Demand
    & Telecom, DSP companies
    & Semiconductor, EDA, VLSI companies (higher demand) \\
  Overall Placement
    & Excellent (top NIT)
    & Very good (strong regional industry connections) \\
  Recommendation
    & \multicolumn{2}{l}{Choose based on your interest in the domain; both are
      excellent choices.} \\
  \bottomrule
\end{tblr}
