%% ============================================================
%%  chapters/05_cutoffs.tex
%%  Chapter 5: GATE Score & Cutoff Analysis
%% ============================================================

\chapter{GATE Score \& Cutoff Analysis}
\label{chap:cutoffs}

%% ─────────────────────────────────────────────────────────
\section{IIT / IISc Cutoffs for VLSI Branches}
\label{sec:iit-cutoffs}

\begin{tblr}{
    colspec  = {X[3,l] X[2,l] X[3,l] X[3,l]},
    hlines, vlines,
    row{1}   = {bg=pfBlue, fg=white, font=\sffamily\bfseries},
    row{2,4,6,8,10} = {bg=pfGrey},
  }
  \toprule
  Institute & Branch & UR Cutoff (Score) & Notes \\
  \midrule
  \inst{IISc Bangalore}
    & MVLSI
    & \cutoff{900}
    & Typically remains above 900 for UR in early rounds. \\
  \inst{IISc Bangalore}
    & ESE
    & \cutoff{850}
    & Slightly lower than MVLSI. \\
  \inst{IIT Bombay}
    & ICS
    & \cutoff{900}
    & Highly competitive; falls slightly in later rounds. \\
  \inst{IIT Bombay}
    & ESE
    & \cutoff{850}
    & \\
  \inst{IIT Madras}
    & ICS
    & \cutoff{850}
    & \\
  \inst{IIT Delhi}
    & IEC
    & \cutoff{720} -- 687
    & General cutoff starts $\sim$720; drops to $\sim$687 in final rounds. \\
  \inst{IIT Hyderabad}
    & VLSI
    & $\sim$650 (late rounds)
    & Significantly lower in final rounds. \\
  \bottomrule
\end{tblr}

\begin{protip}[Top-5 IITs + IISc General Rule]
  For the top-5 IITs and IISc, an approximate cutoff of \textbf{720+ GATE score}
  applies for General category candidates during the first 6 rounds. Cutoffs drop
  considerably in the final rounds.
\end{protip}

%% ─────────────────────────────────────────────────────────
\section{Official Cutoff References}
\label{sec:official-refs}

For official and updated cutoff data, refer to:

\begin{pfActionList}
  \item \textbf{IISc:}
        \url{https://iisc.ac.in/admissions/cut-off-report-and-gate-score-of-previous-years/}
  \item \textbf{IIT Madras:}
        \url{https://mtechadm.iitm.ac.in/pdfs/M.Tech.2024_Cutoff.pdf}
  \item \textbf{IIT Kanpur (2024):}
        \url{https://iitk.ac.in/ee/data/admissions/2024-25/Shorlist_Criteria-01-07-24.pdf}
  \item \textbf{IIT Kanpur (2023):}
        \url{https://www.iitk.ac.in/ee/data/admissions/2023-24/6_Shorlist_Criteria-26-06-23.pdf}
  \item \textbf{NITs (CCMT 2025 Community Sheet):}
        \url{https://docs.google.com/spreadsheets/d/1G0KjJN9MNMiwWDRDf4OrzgEBYivGnn_lT0G7jK57ikk}
\end{pfActionList}

%% ─────────────────────────────────────────────────────────
\section{PSU Cutoff Reference}
\label{sec:psu-cutoffs}

\begin{tblr}{
    colspec = {X[3,l] X[2,l] X[4,l]},
    hlines, vlines,
    row{1} = {bg=pfBlue, fg=white, font=\sffamily\bfseries},
    row{2,4,6,8} = {bg=pfGrey},
  }
  \toprule
  PSU & Category & Approximate Cutoff \\
  \midrule
  NTPC    & General  & Rank $\lesssim$150 safe for top PSUs \\
  NTPC    & OBC      & Round 2: approx.\ rank 1118 \\
  CIL     & OBC      & Round 3 availability at rank $\sim$1300--1400 \\
  NPCIL   & OBC      & 563 \GATE score (2024 cutoff) \\
  \bottomrule
\end{tblr}

%% ─────────────────────────────────────────────────────────
\section{Low Score Options (40 marks / $\sim$560 score)}
\label{sec:low-score}

\begin{deadline}[Opportunities at $\sim$40 Marks in GATE ECE]
  \begin{pfChecklist}
    \item \textbf{PhD at IITs/IISc:} Interview cutoffs for PhD are very low;
          admission is entirely based on the interview performance.
    \item \textbf{NIT VLSI branches via CCMT:} Check round-wise cutoffs on the
          CCMT portal; institutes like NIT Kurukshetra have good industry
          connections.
    \item \textbf{BITS Pilani HD program:} A strong option if fees are not a
          constraint (see Chapter~\ref{chap:alternatives}).
    \item \textbf{NIT Kurukshetra example:} Proven track record of students
          securing internships and FTE offers despite being a newer-tier NIT.
  \end{pfChecklist}
\end{deadline}
