%% ============================================================
%%  chapters/06_financial.tex
%%  Chapter 6: Financial & Loan-Related Queries
%% ============================================================

\chapter{Financial \& Loan-Related Queries}
\label{chap:financial}

%% ─────────────────────────────────────────────────────────
\section{Fee Waivers \& Scholarships}
\label{sec:waivers}

\begin{eligalert}[EWS / Low-Income Students]
  \textbf{EWS (Economically Weaker Section)} students receive \textbf{almost
  full tuition fee waivers} at most IITs. Additionally, scholarships are
  available that can effectively sponsor the entire 2-year M.Tech course.
  Apply for EWS certificate well in advance of counseling.
\end{eligalert}

%% ─────────────────────────────────────────────────────────
\section{Admission Fee Management}
\label{sec:admission-fee}

\begin{faqentry}{Do all IITs require a \rupee 1000 admission fee?
  How can such expenses be managed?}
  Most IITs charge a non-refundable application fee in the \rupee 500--1500 range.
  When applying to multiple institutes, these costs add up. Strategies:
  \begin{pfChecklist}
    \item Apply selectively---choose institutes where your \GATE score is
          competitive.
    \item Note that the application fee is separate from the seat acceptance fee
          (which is refundable upon seat surrender in most cases).
    \item Education loans from nationalized banks can be availed before final
          admission confirmation in many cases; consult your bank branch directly.
  \end{pfChecklist}
\end{faqentry}

%% ─────────────────────────────────────────────────────────
\section{Self-Sponsored Courses}
\label{sec:self-sponsored}

Several IITs and NITs offer \textbf{self-sponsored / industry-sponsored} M.Tech
seats with \textbf{significantly higher fee structures} but the same degree.
These are designed for working professionals or candidates who miss the
GATE-scholarship cutoff.

\begin{pfActionList}
  \item IIT Hyderabad, IIT Jodhpur, IIT Gandhinagar
  \item NIT Surathkal (NIT Karnataka)
  \item Check individual institute portals for exact fee structures and
        eligibility criteria.
\end{pfActionList}
