%% ============================================================
%%  chapters/07_research_ms.tex
%%  Chapter 7: Research & MS Programs
%% ============================================================

\chapter{Research \& MS Programs}
\label{chap:research}

%% ─────────────────────────────────────────────────────────
\section{M.Tech Research vs.\ M.Tech (2-Year)}
\label{sec:mtech-research}

\begin{tblr}{
    colspec = {X[3,l] X[3,l] X[3,l]},
    hlines, vlines,
    row{1} = {bg=pfBlue, fg=white, font=\sffamily\bfseries},
    row{2,4,6,8} = {bg=pfGrey},
  }
  \toprule
  Factor & M.Tech TA (2 years) & M.Tech RA / Research (3 years min.) \\
  \midrule
  Duration   & 2 years & 3+ years \\
  Stipend    & \rupee 12,400/month & \rupee 13,400/month (approx.) \\
  Course Load & Higher & Lower (more project-focused) \\
  Research Output & Moderate & Higher (paper publications, PhD pathway) \\
  Placements & Good & Same placement access at end of course \\
  Guide      & Optional & Must identify before joining \\
  \bottomrule
\end{tblr}

\begin{protip}[M.Tech Research Advantage]
  M.Tech Research is an excellent pathway to a \textbf{PhD from reputed
  institutes in India or abroad}. The research-focused environment enables
  high-quality project work and better paper publication opportunities.
\end{protip}

%% ─────────────────────────────────────────────────────────
\section{Should I Pursue MS with a Low GATE Score?}
\label{sec:ms-low-score}

\begin{faqentry}{Should I pursue MS if I have a low GATE score?}
  Yes. Students with lower \GATE scores still have MS admission opportunities,
  especially at newer IITs. While \GATE score is the primary criterion,
  \textbf{interviews and undergraduate projects} also significantly influence
  selection for MS programs. Prepare your projects well and aim for a strong
  interview performance.
\end{faqentry}

%% ─────────────────────────────────────────────────────────
\section{Statement of Purpose (SOP)}
\label{sec:sop}

\begin{faqentry}{Does the MS program require an SOP?}
  Yes, most research-based MS programs (especially at IISc) require an SOP as
  part of the application. The SOP should clearly articulate:
  \begin{pfChecklist}
    \item Your research interests and why you have chosen this area.
    \item Relevant UG projects, publications, or internships.
    \item Your long-term career goals.
    \item Why this specific institute and research group.
  \end{pfChecklist}
\end{faqentry}

%% ─────────────────────────────────────────────────────────
\section{Scope of M.Tech Research in ECE at IISc}
\label{sec:iisc-research}

The \textbf{M.Tech Research} program at IISc is research-intensive with a
reduced course load compared to the 2-year M.Tech. Key features:

\begin{pfChecklist}
  \item Work under a specific guide in a domain of your research interest.
  \item Excellent pathway for PhD admissions globally.
  \item IISc's strong publication culture means high-impact research output
        is achievable during the program.
  \item For \textbf{Photonic Integrated Circuits} research: IISc has dedicated
        labs; check the DESE department for relevant faculty.
  \item Placement opportunities exist at the end of the program for students
        who wish to enter industry.
\end{pfChecklist}
