%% ============================================================
%%  chapters/08_drop_guidance.tex
%%  Chapter 8: Drop Year & Career Guidance
%% ============================================================

\chapter{Drop Year \& Career Guidance}
\label{chap:drop}

%% ─────────────────────────────────────────────────────────
\section{Should I Take a Drop?}
\label{sec:drop}

\begin{faqentry}{Should I take a drop or join a self-sponsored NIT program?}
  If this was your \textbf{first attempt} and you have genuine interest in
  pursuing M.Tech from an IIT/IISc for the long-term career benefits:
  \begin{pfChecklist}
    \item Taking a drop is a reasonable decision.
    \item Top branches at NITs like Trichy and Warangal also offer excellent
          placements if you don't wish to drop.
    \item Self-sponsored programs at top NITs are valid if you have no desire
          to re-attempt \GATE.
  \end{pfChecklist}

  \noindent Key question to ask yourself: \textit{Do I genuinely want to be in
  the tech domain and pursue research/high-end engineering, or am I seeking a
  stable job?} Your answer determines whether a drop is worthwhile.
\end{faqentry}

%% ─────────────────────────────────────────────────────────
\section{What If I Don't Qualify for GATE?}
\label{sec:didnt-qualify}

\begin{protip}[Stay Motivated]
  Not clearing \GATE is not the end. Identify your mistakes in this attempt,
  rectify your weak areas, and adopt an organized and structured preparation
  strategy for the next attempt.
\end{protip}

Immediate next steps:
\begin{pfActionList}
  \item Analyze your GATE answer key and pinpoint subject-wise weaknesses.
  \item Join a structured study group or coaching if self-study hasn't worked.
  \item Consider attempting in the next year with focused preparation.
\end{pfActionList}

%% ─────────────────────────────────────────────────────────
\section{SSC JE Alongside M.Tech?}
\label{sec:ssc-mtech}

\begin{eligalert}[Important Caution]
  Preparing for \textbf{SSC JE} or other government exams simultaneously with an
  M.Tech program is generally a \textbf{poor choice}. It divides your attention
  and compromises performance in both.
  \begin{pfChecklist}
    \item If your primary interest is government sector jobs, SSC JE may be a
          direct and efficient path.
    \item Joining M.Tech purely as a backup while preparing for other exams
          wastes the resources and opportunities the M.Tech provides.
    \item Make a clear decision: M.Tech for tech growth \textbf{or} SSC JE for
          government jobs.
  \end{pfChecklist}
\end{eligalert}

%% ─────────────────────────────────────────────────────────
\section{Other Options If Not IIT/NIT}
\label{sec:other-options}

\begin{tblr}{
    colspec = {X[3,l] X[5,l]},
    hlines, vlines,
    row{1} = {bg=pfBlue, fg=white, font=\sffamily\bfseries},
    row{2,4,6,8} = {bg=pfGrey},
  }
  \toprule
  Option & Notes \\
  \midrule
  \inst{IIITs} (Hyderabad, Delhi, etc.)
    & Strong tech culture; IIIT-H in particular has excellent placement records. \\
  \inst{BITS Pilani} (HD program)
    & Working professional program; no GATE needed; see Chapter~\ref{chap:alternatives}. \\
  \inst{Jadavpur University (JU)}
    & Reputable institution; good for candidates in eastern India. \\
  \inst{DTU Delhi}
    & Decent option; own entrance exam; good for Delhi-based candidates. \\
  MS from abroad (NUS / Germany)
    & Strong option for high-achieving students open to international education. \\
  \bottomrule
\end{tblr}
