%% ============================================================
%%  frontmatter/acknowledgements.tex
%% ============================================================

\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
\markboth{Acknowledgements}{}

A heartfelt thanks to every \PrepFusion student who took the time to share their
valuable insights, interview experiences, and counseling data. Your contributions
have made this guide possible.

\vspace{1em}

\noindent\textbf{Special Thanks to:}

\begin{pfChecklist}
  \item \textbf{Srijan Dwivedi} --- Extensive contributions on CFTI mode, GATE
        cutoffs, and PSU recruitment analysis.
  \item \textbf{Palak Agarwal} --- Insights on GATE counseling timelines,
        MS program queries, and IIT analog research.
  \item \textbf{Sangrag} --- Comprehensive answers covering PSU recruitment
        processes, COAP/CCMT workflows, and interview strategies.
  \item \textbf{Nilimay} --- Contributions to interview preparation strategies.
  \item \textbf{Ravi} --- Detailed interview question bank (Digital, Analog,
        Control Systems).
  \item \textbf{Deepto (Deeptapol)} --- PSU career growth insights and
        preparation strategies.
  \item \textbf{Anish} --- NIT cutoff data compilation and interview prep tips.
\end{pfChecklist}

\vspace{1em}

\noindent\textit{And to all other \PrepFusion community members who contributed
anonymously---your effort is deeply appreciated.}

\vspace{2em}

\begin{center}
  \href{https://prepfusion.in}{\textcolor{pfBlue}{\textbf{www.PrepFusion.in}}}
  \qquad
  \href{https://youtube.com/@PrepFusion-GATE}{YouTube: \textbf{@PrepFusion-GATE}}
\end{center}
