%% ============================================================
%%  frontmatter/disclaimer.tex
%% ============================================================

\chapter*{Disclaimer}
\addcontentsline{toc}{chapter}{Disclaimer}
\markboth{Disclaimer}{}

\begin{disclaimer}
  The information provided in this document has been gathered from various sources
  and is intended for general guidance and informational purposes only. While every
  effort has been made to ensure the accuracy and reliability of the content,
  \PrepFusion \textbf{does not} guarantee the completeness, correctness, or
  timeliness of the information provided.

  The resources, suggestions, and recommendations included are based on our
  understanding and interpretation of the available data. However,
  \PrepFusion \textbf{is not responsible} for any errors, omissions, or outcomes
  resulting from the use of this information. Users are advised to independently
  verify any critical details---such as admission cutoffs, counseling processes,
  or PSU recruitment criteria---from \textbf{official sources} or relevant
  authorities.

  This document does not constitute professional advice, and \PrepFusion
  \textbf{shall not be held liable} for any decisions made or actions taken based
  on the information provided herein. Users are solely responsible for their
  choices and outcomes.

  By using this document, you acknowledge and agree that \PrepFusion is not
  responsible for any consequences, direct or indirect, arising from its use.
\end{disclaimer}

\vspace{1em}
\noindent
\textbf{This document is dynamic and will be continuously updated as new
information is received from the PrepFusion student community.}
